---
title: "Support Vector Machines with Beer"
author: "Ryan Volkert"
date: "December 9, 2019"
output:
  beamer_presentation:
    colortheme: "dove"
    fonttheme: "serif"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}

---

```{r setup, include=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(e1071)
library(kableExtra)
library(bookdown)

source('beersvm.R')
```

## First Look

* Collected from CraftCans.com via Kaggle
* 100 distint types of beer
* Several had to do with region
* Condensed to 12 beers

```{r}
kable(head(beer %>%
             filter(!is.na(ibu))),
      format='latex', booktabs=T) %>%
  kable_styling(latex_options='scale_down')
```

## Summary Statistics

\begin{columns}
\column{.5\textwidth}

```{r}
beer %>%
  filter(!is.na(ibu)) %>%
  select(abv, ibu, ounces) %>%
  summarize_all(list(~min(.), ~max(.), ~mean(.))) %>%
  gather(stat, val) %>%
  separate(stat, into=c('var','stat'), sep='_') %>%
  spread(stat, val) %>%
  select(var, mean, max, min) %>%
  kable(format='latex', booktabs=T) %>%
  kable_styling(latex_options='scale_down')
```

\column{.5\textwidth}

```{r}
beer %>%
  group_by(style) %>%
  summarize(n()) %>%
  kable(format='latex',
        col.names = c('style', 'count'),
        booktabs=T) %>%
  kable_styling(full_width=T)
```

\end{columns}

---

```{r}
beer %>%
  filter(style!='Other',
         style!='Misc. Ale') %>%
  ggplot() +
  geom_point(aes(abv, ibu, color = style))
```

## Full SVM

```{r}
kable(table(pred_full, beer$style), booktabs=T) %>%
  kable_styling(latex_options='scale_down')
```

## IPA, APA, and Pale Ale

```{r}
ggplot(pa) +
  geom_point(aes(abv, ibu, color=style))
```

---

```{r}
kable(table(pred_pa, pa$style),
      booktabs=T) %>%
  kable_styling(full_width=T)
```

---

```{r}
plot(svm_pa, pa, ibu ~ abv)
```

## Lager and Porter

```{r}
beer %>%
  filter(style=='Lager' |
           style=='Porter') %>%
  ggplot() +
  geom_point(aes(abv, ibu, color=style))
```

---

```{r}
kable(table(pred_lp, lp$style),
      booktabs=T) %>%
  kable_styling(full_width=T)
```

---

```{r}
plot(svm_lp, lp, ibu~abv)
```

## Ales

```{r}
ggplot(ales) +
  geom_point(aes(abv, ibu, color=style))
```

---

```{r}
kable(table(pred_ales, ales$style),
      booktabs=T) %>%
  kable_styling(full_width=T)
```

---

```{r}
plot(svm_ales, ales, ibu~abv)
```

## Conclusion

* Data only included *abv* and *ibu*
* Another indicator, such as *color*, may have separated the data more clearly
* Maybe yeast and fermentation type is the only true indicator